|

### 2021-02-07 appendix/appendix.Rmd
change tables, add some models

\footnotesize
```{r loading, warning=F, message=F, error=F, cache=T}
# Install and load required packages
packages <- c("cjoint", "cregg", "kableExtra",
              "janitor", "stargazer", "tidyverse")
installed_packages <- packages %in% rownames(installed.packages())
if (any(installed_packages == FALSE)) {
  install.packages(packages[!installed_packages])
}
invisible(lapply(packages, library, character.only = TRUE))

@@

m1 <- lm(exp02_outcomes ~ exp02_police_treat, data = df_exp02)
m1cov <- coeftest(m1, vcov = vcovHC(m1, type = "HC1"))
m1se <- sqrt(diag(m1cov))

m2 <- lm(exp02_outcomes ~ exp02_slow_justice_treat, data = df_exp02)
m2cov <- coeftest(m2, vcov = vcovHC(m2, type = "HC1"))
m2se <- sqrt(diag(m2cov))

m3 <- lm(exp02_outcomes ~ exp02_small_punishment_treat, data = df_exp02)
m3cov <- coeftest(m3, vcov = vcovHC(m3, type = "HC1"))
m3se <- sqrt(diag(m3cov))

m4 <- lm(exp02_outcomes ~ exp02_any_treat, data = df_exp02)
m4cov <- coeftest(m4, vcov = vcovHC(m4, type = "HC1"))
m4se <- sqrt(diag(m4cov))

stargazer(m1, m2, m3, m4, se = list(m1se, m2se, m3se, m4se), header = FALSE,
          title = "Experiment 02 -- Main Results", align = TRUE, label = "tab:exp02main",
          dep.var.caption = "\\textit{Dependent Variable}", dep.var.labels = "Lynching Support",
          covariate.labels = c("Police does not patrol area", "Justice too slow",
                               "Punishment not harsh enough", "Combined treatments"),
          column.sep.width = "3pt", notes = "Robust standard error in parentheses.",
          keep.stat = c("n", "rsq"), no.space = TRUE, font.size = "footnotesize")
```
\normalsize

@@

```{r exp02-demographics, warning=F, message=F, error=F, cache=T, fig.pos="H", results='asis'}
df_exp02_group <- df_exp02 %>%
  filter(gender == c("Female", "Male"),
         race %in% c("Asian", "Black", "Mixed Race", "White"),
         education %in% c("College", "Graduate School",
                          "Primary School", "Secondary School", "High School")) %>%
  mutate(education2 = case_when(education == "Primary School" ~ "Primary or Secondary School",
                                education == "Secondary School" ~ "Primary or Secondary School",
                                TRUE ~ as.character(education))) %>%
  mutate(household_income2 = case_when(household_income == "Up to R$1,000" ~ "Up to R$3,000",
                                       household_income == "From R$1,001 to R$2,000" ~ "Up to R$3,000",
                                       household_income == "From R$2,001 to R$3,000" ~ "Up to R$3,000",
                                       household_income == "From R$3,001 to R$5,000" ~ "From R$3,001 to R$5,000",
                                       household_income == "From R$5,001 to R$10,000" ~ "Above R$5,000",
                                       household_income == "From R$10,001 to R$20,000" ~ "Above R$5,000",
                                       household_income == "Above R$20,000" ~ "Above R$5,000",
                                       TRUE ~ NA_character_))

m1 <- lm(exp02_outcomes ~ gender, data = df_exp02_group)
m1cov <- coeftest(m1, vcov = vcovHC(m1, type = "HC1"))
m1se <- sqrt(diag(m1cov))

m2 <- lm(exp02_outcomes ~ age, data = df_exp02_group)
m2cov <- coeftest(m2, vcov = vcovHC(m2, type = "HC1"))
m2se <- sqrt(diag(m2cov))

m3 <- lm(exp02_outcomes ~ race, data = df_exp02_group)
m3cov <- coeftest(m3, vcov = vcovHC(m3, type = "HC1"))
m3se <- sqrt(diag(m3cov))

m4 <- lm(exp02_outcomes ~ education2, data = df_exp02_group)
m4cov <- coeftest(m4, vcov = vcovHC(m4, type = "HC1"))
m4se <- sqrt(diag(m4cov))

m5 <- lm(exp02_outcomes ~ household_income2, data = df_exp02_group)
m5cov <- coeftest(m5, vcov = vcovHC(m5, type = "HC1"))
m5se <- sqrt(diag(m5cov))

m6 <- lm(exp02_outcomes ~ ideology, data = df_exp02_group)
m6cov <- coeftest(m6, vcov = vcovHC(m6, type = "HC1"))
m6se <- sqrt(diag(m6cov))

m7 <- lm(exp02_outcomes ~ previous_victim_dummy, data = df_exp02_group)
m7cov <- coeftest(m7, vcov = vcovHC(m7, type = "HC1"))
m7se <- sqrt(diag(m7cov))

m8 <- lm(exp02_outcomes ~ views_police, data = df_exp02_group)
m8cov <- coeftest(m8, vcov = vcovHC(m8, type = "HC1"))
m8se <- sqrt(diag(m8cov))

m9 <- lm(exp02_outcomes ~ views_justice, data = df_exp02_group)
m9cov <- coeftest(m9, vcov = vcovHC(m9, type = "HC1"))
m9se <- sqrt(diag(m9cov))

stargazer(m1, m2, m3, m4, m5, se = list(m1se, m2se, m3se, m4se, m5se), header = FALSE,
          align = TRUE, label = "exp02demo1",
          title = "Experiment 02 -- Effect of Demographic Characteristics on Lynching Support", 
          dep.var.caption = "\\textit{Dependent Variable}", dep.var.labels = "Lynching Support",
          covariate.labels = c("Male", "Age (years)", "Black", "Mixed Race",
                               "White", "Graduate School", "High School",
                               "Primary or Secondary School", ""),
          column.sep.width = "3pt", notes = "Robust standard error in parentheses.",
          keep.stat = c("n", "rsq"), no.space = TRUE)

stargazer(m6, m7, m8, m9, se = list(m6se, m7se, m8se, m9se), header = FALSE,
          title = "Experiment 02 -- Effect of Demographic Characteristics on Lynching Support", 
dep.var.caption = "\\textit{Dependent Variable}", dep.var.labels = "Lynching Support",
column.sep.width = "3pt", notes = "Robust standard error in parentheses.",
keep.stat = c("n", "rsq"), no.space = TRUE)
```

>>>>

\footnotesize
```{r loading, warning=F, message=F, error=F, cache=T}
# Install and load required packages
packages <- c("cjoint", "cregg", "estimatr", "kableExtra",
              "janitor", "stargazer", "tidyverse")
installed_packages <- packages %in% rownames(installed.packages())
if (any(installed_packages == FALSE)) {
  install.packages(packages[!installed_packages])
}
invisible(lapply(packages, library, character.only = TRUE))

@@

m1 <- lm(exp02_outcomes ~ exp02_police_treat, data = df_exp02)
m2 <- lm(exp02_outcomes ~ exp02_slow_justice_treat, data = df_exp02)
m3 <- lm(exp02_outcomes ~ exp02_small_punishment_treat, data = df_exp02)
m4 <- lm(exp02_outcomes ~ exp02_any_treat, data = df_exp02)

stargazer(m1, m2, m3, m4, se = starprep(m1, m2, m3, m4),
          p = starprep(m1, m2, m3, m4, se_type = "HC2", stat = "p.value"),
          header = FALSE, align = TRUE, label = "exp02main",
          title = "Experiment 02 -- Main Results", style = "apsr",
          dep.var.labels = "Lynching Support",
          covariate.labels = c("Police does not patrol area", "Justice too slow",
                               "Punishment not harsh enough", "Combined treatments"),
          column.sep.width = "3pt", notes = "Robust standard errors in parentheses.",
          keep.stat = "n", no.space = TRUE, font.size = "footnotesize")
```
\normalsize

@@

\footnotesize
```{r exp02-demographics, warning=F, message=F, error=F, cache=T, fig.pos="H", results='asis'}
df_exp02_group <- df_exp02 %>%
  filter(gender == c("Female", "Male"),
         race %in% c("Asian", "Black", "Mixed Race", "White", "Indigenous"),
         education %in% c("College", "Graduate School", "Primary School",
                          "Secondary School", "High School")) %>%
  mutate(race = fct_relevel(race, "White", "Black", "Mixed Race", "Asian",
                            "Indigenous")) %>%
  mutate(education2 = case_when(education == "Primary School" ~ "Primary or Secondary School",
                                education == "Secondary School" ~ "Primary or Secondary School",
                                TRUE ~ as.character(education)),
         education2 = fct_relevel(education2, "Primary or Secondary School",
                                  "High School", "College", "Graduate School")) %>%
  mutate(views_police = fct_relevel(views_police, "Regular", "Very Good", "Good",
                                    "Bad", "Very Bad")) %>%
  mutate(views_justice = fct_relevel(views_justice, "Regular", "Very Good", "Good", 
                                    "Bad", "Very Bad")) %>%
  mutate(ideology = fct_relevel(ideology, "Center", "Left", "Center-Left",
                                "Center-Right", "Right", "Don't Know",
                                "Rather Not Say")) %>%
  mutate(household_income2 = case_when(household_income == "Up to R$1,000" ~ "Up to R$3,000",
                                       household_income == "From R$1,001 to R$2,000" ~ "Up to R$3,000",
                                       household_income == "From R$2,001 to R$3,000" ~ "Up to R$3,000",
                                       household_income == "From R$3,001 to R$5,000" ~ "From R$3,001 to R$5,000",
                                       household_income == "From R$5,001 to R$10,000" ~ "Above R$5,000",
                                       household_income == "From R$10,001 to R$20,000" ~ "Above R$5,000",
                                       household_income == "Above R$20,000" ~ "Above R$5,000",
                                       TRUE ~ NA_character_),
  household_income2 = fct_relevel(household_income2, "Up to R$3,000", "From R$3,001 to R$5,000",
                                  "Above R$5,000"))

# Models
m1 <- lm(exp02_outcomes ~ gender, data = df_exp02_group)
m2 <- lm(exp02_outcomes ~ age, data = df_exp02_group)
m3 <- lm(exp02_outcomes ~ race, data = df_exp02_group)
m4 <- lm(exp02_outcomes ~ education2, data = df_exp02_group)
m5 <- lm(exp02_outcomes ~ household_income2, data = df_exp02_group)
m6 <- lm(exp02_outcomes ~ ideology, data = df_exp02_group)
m7 <- lm(exp02_outcomes ~ previous_victim_dummy, data = df_exp02_group)
m8 <- lm(exp02_outcomes ~ views_police, data = df_exp02_group)
m9 <- lm(exp02_outcomes ~ views_justice, data = df_exp02_group)

# Tables (robust standard errors from estimatr)
stargazer(m1, m2, m3, m4, m5, se = starprep(m1, m2, m3, m4, m5),
          p = starprep(m1, m2, m3, m4, m5, se_type = "HC1", stat = "p.value"),
          header = FALSE, align = TRUE, label = "exp02demo1",
          title = "Experiment 02 -- Demographic Characteristics and Lynching Support",
          dep.var.labels = "Lynching Support",
          covariate.labels = c("Male", "Age (years)", "Black", "Mixed race",
                               "Asian", "Indigenous", "High school", "College",
                               "Graduate school", "3,001 to 5,000 BRL",
                               "5,000+ BRL"), style = "apsr",
          column.sep.width = "2pt", notes = c("Reference categories: Model 1: Female; 
                                              Model 3: White; Model 4: Primary or secondary school;",
                                              "Model 5: Up to 3,000 BRL. Robust standard errors in
                                              parentheses."),
          keep.stat = "n", no.space = TRUE, font.size = "footnotesize")

stargazer(m6, m7, m8, m9, se = starprep(m6, m7, m8, m9),
          p = starprep(m6, m7, m8, m9, se_type = "HC2", stat = "p.value"),
          header = FALSE, align = TRUE, label = "exp02demo2",
          title = "Experiment 02 -- Demographic Characteristics and Lynching Support",
          dep.var.labels = "Lynching Support", style = "apsr",
          covariate.labels = c("Left", "Center-Left", "Center-Right", "Right")
          column.sep.width = "2pt", notes = "Robust standard error in parentheses.",
          keep.stat = c("n", "rsq"), no.space = TRUE, font.size = "footnotesize")
```
\normalsize
